Final Project Data 205

### 2021-12-03 Draft Final Project1.Rmd
Add files via upload

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021")

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"

time_periods <- c("December-2020","November-2020","October-2020","September-2020", "August-2020", "July-2020", "June-2020","May-2020","April-2020","March-2020","February-2020","January-2020")

@@

# Create Plot
```{r}
df.groupby('year').type.value_counts().unstack(0).plot.barh()

@@

>>>>

url <- "https://www.wmata.com/about/transit-police/upload/Monthly-Blotter-"
time_periods <- c("October-2021","September-2021", "August-2021", "July-2021", "June-2021","May-2021","April-2021","March-2021","February-2021","January-2021","December-2020","November-2020","October-2020","September-2020", "August-2020")

url <-"https://www.wmata.com/about/transit-police/upload/June-2020-Blotter-Report"

@@

## Clean the WMATA data with NA's
```{r}

@@

# Create Groupby Year & State (test)
```{r}
df_state<- df_wmata %>%
group_by(year) %>%
select(DC,MD,VA)
summarize(sum = sum(state), count = n()) %>%
arrange(year, state)

df_state
```

# Create Plot on the Crimes Committed by State
```{r}

```
# Creat a Groupby type & count (tester)
```{r}
df_wmata %>%                         # Count rows by group
  group_by(type) %>% 
  summarize(n = n())
```

```{r}
df_type <-df_wmata
  group_by(type)
df_type
```

```{r}
df_type<- df_wmata %>%
 group_by(type) %>%
    summarize(count=n())

# Create Plot on Type of Crimes by Type
```{r}
ggplot(df_wmata, aes(x=type, fill=type )) + 
  geom_bar( ) +
  scale_fill_hue(c = 40) +
  theme(legend.position="none")
```

# Create Plot on 
```{r}

#Census Data 
```{r}
library(httr)
library(jsonlite)
library(tidyverse)

# Import json data from Census API
data <- GET("https://api.census.gov/data/2019/acs/acs1/?get=NAME,B01001_001E,B01002_001E,C22001_001E,B25064_001E&for=county:*&in=state:24")
data <- content(data, as="text")

# Load into a data frame
df <- fromJSON(data)
class(df)
head(df)

# Change to tibble
df <- as_tibble(df)
head(df)

# Make first row column header names
names(df) <- c(df[1,])
head(df)

# Keep all but first row (which had the column header names)
df <- df[-1,]
head(df)

# Rename columns as needed
names(df) <- c('NAME',
               'B01001_001E' = 'Population',
               'B01002_001E' = 'Median_Age',
               'C22001_001E' = 'Household_Poverty',
               'B25064_001E' = 'Median_Gross_Rent',
               'state',
               'county')
head(df)
